---
title: "Whippo et al Code for Posting"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

Libraries
```{r, echo = TRUE}
library(vegan)
#library(Rcmdr)
#library(BiodiversityR)
library(plyr)
library(reshape2)
library(dplyr)
library(MuMIn)
library(lubridate)
library(ggplot2)
library(purrr)
library(knitr)
```

Load data
```{r, echo = TRUE}
data.tr <- read.csv("../data/Whippodata.csv")
data.tr <- data.tr[,-1]
sites <- read.csv("../data/site.info.csv")
```

From full datasets of all sites, species and sampling dates, subset data:

1. Remove all taxa that are not epifauna: 
```{r}
# levels(data.tr$eelgrss.epifauna)
data.e <- data.tr %>% filter(eelgrss.epifauna == "yes" | eelgrss.epifauna == "sometimes")
data.n <- data.tr %>% filter(eelgrss.epifauna == "no")
data.tr <- data.e #reset to data.e
```

2. Create data subsets for different sampling times
```{r, echo = TRUE}
# 5 sites were sampled in May, June and July
dataMAY <- data.tr[(data.tr$Time.Code2=="A"),]
dataJULY <- data.tr[(data.tr$Time.Code2=="C" & data.tr$site!="BE" & data.tr$site!="EI" & data.tr$site!="CC" & data.tr$site!="BI"),]
dataAUG <- data.tr[(data.tr$Time.Code2=="E"),]

# this set has all three sampling times for the 5 sites sampled 3 times
data3times <- data.tr[(data.tr$site!="BE" & data.tr$site!="EI" & data.tr$site!="CC" & data.tr$site!="BI"),]

# this set has the 9 sites sampled in July
dataJULY9 <- data.tr[(data.tr$Time.Code2=="C"),]
```

3. Create site-level data by collapsing across plots. Change the data used in start data to consider other temporal subsets.
```{r, ech = TRUE}
start.data <- dataJULY9 # dataMAY, dataAUG, dataJULY, data3times
data.ms <- ddply(start.data, .(TimeID, area, species), summarise, sum(abundance)) #order
data2 <- dcast(data.ms, TimeID ~ species, mean) #order
```

Table 1: Site-level results for July

1. Diversity (Gamma) Observed number of species per site for month identified in start.data: 
```{r}
# dim(data2)
data.alpha <- data2
data.alpha <- specnumber(data.alpha[,2:35])
site.alpha <- as.data.frame(cbind(as.character(data2$TimeID), data.alpha))
names(site.alpha) <- c("site.time", "alpha")
site.alpha$site <- c("BE", "BI", "CB", "CC", "DC", "EI", "NB", "RP", "WI") # c("CB", "DC", "NB", "RP", "WI") # 
kable(site.alpha, caption = "Observed Number of Species at each site on sample date indicated in column site.time. This information is in the 'Diversity' column in Table 1.")
```

Create the data file we will use for univariate diversity indices and ranks:
```{r}
div.data <- dcast(start.data[,c(1:4,12)], site + Date + Sample ~ species, sum)
```


2. Morisita's index (aggregation)
```{r}
### Morisita's I within meadows for column Im
I.BE <- dispindmorisita(div.data[(div.data$site=='BE'),-(c(1:3,38:39))], unique.rm = TRUE, na.rm = TRUE)
I.RP <- dispindmorisita(div.data[(div.data$site=='RP'),-(c(1:3,38:39))], unique.rm = TRUE, na.rm = TRUE)
I.DC <- dispindmorisita(div.data[(div.data$site=='DC'),-(c(1:3,38:39))], unique.rm = TRUE, na.rm = TRUE)
I.WI <- dispindmorisita(div.data[(div.data$site=='WI'),-(c(1:3,38:39))], unique.rm = TRUE, na.rm = TRUE)
I.CB <- dispindmorisita(div.data[(div.data$site=='CB'),-(c(1:3,38:39))], unique.rm = TRUE, na.rm = TRUE)
I.CC <- dispindmorisita(div.data[(div.data$site=='CC'),-(c(1:3,34:35))], unique.rm = TRUE, na.rm = TRUE)
I.EI <- dispindmorisita(div.data[(div.data$site=='EI'),-(c(1:3,38:39))], unique.rm = TRUE, na.rm = TRUE)
I.NB <- dispindmorisita(div.data[(div.data$site=='NB'),-(c(1:3,38:39))], unique.rm = TRUE, na.rm = TRUE)
I.BI <- dispindmorisita(div.data[(div.data$site=='BI'),-(c(1:3,38:39))], unique.rm = TRUE, na.rm = TRUE)

## assemble mean I values, and confidence intervals for TABLE 1
means <- c(mean(I.DC[,4], na.rm = TRUE), mean(I.WI[,4], na.rm = TRUE), mean(I.BE[,4], na.rm = TRUE), mean(I.EI[,4], na.rm = TRUE), mean(I.RP[,4], na.rm = TRUE), mean(I.NB[,4], na.rm = TRUE), mean(I.CB[,4], na.rm = TRUE), mean(I.BI[,4], na.rm = TRUE), mean(I.CC[,4], na.rm = TRUE))

ci.upper <- function(x) mean(x) + 1.96*sd(x)/sqrt(length(x))
ci.lower <- function(x) mean(x) - 1.96*sd(x)/sqrt(length(x))

ci.lowers <- c(ci.lower(I.DC[(I.DC$imst != "NaN"),4]), ci.lower(I.WI[(I.WI$imst != "NaN"),4]), ci.lower(I.BE[(I.BE$imst != "NaN"),4]), ci.lower(I.EI[(I.EI$imst != "NaN"),4]), ci.lower(I.RP[(I.RP$imst != "NaN"),4]), ci.lower(I.NB[(I.NB$imst != "NaN"),4]), ci.lower(I.CB[(I.CB$imst != "NaN"),4]), ci.lower(I.BI[(I.BI$imst != "NaN"),4]), ci.lower(I.CC[(I.CC$imst != "NaN"),4]))

ci.uppers <- c(ci.upper(I.DC[(I.DC$imst != "NaN"),4]), ci.upper(I.WI[(I.WI$imst != "NaN"),4]), ci.upper(I.BE[(I.BE$imst != "NaN"),4]), ci.upper(I.EI[(I.EI$imst != "NaN"),4]), ci.upper(I.RP[(I.RP$imst != "NaN"),4]), ci.upper(I.NB[(I.NB$imst != "NaN"),4]), ci.upper(I.CB[(I.CB$imst != "NaN"),4]), ci.upper(I.BI[(I.BI$imst != "NaN"),4]), ci.upper(I.CC[(I.CC$imst != "NaN"),4]))

Nsig <- c((length(I.DC[(I.DC$pchisq != "NaN" & I.DC$pchisq < 0.01),1])/length(I.DC[(I.DC$imor != "NaN"),1])), (length(I.WI[(I.WI$pchisq != "NaN" & I.WI$pchisq < 0.01),1])/length(I.WI[(I.WI$imor != "NaN"),1])), (length(I.BE[(I.BE$pchisq != "NaN" & I.BE$pchisq < 0.01),1])/length(I.BE[(I.BE$imor != "NaN"),1])), (length(I.EI[(I.EI$pchisq != "NaN" & I.EI$pchisq < 0.01),1])/length(I.EI[(I.EI$imor != "NaN"),1])), (length(I.RP[(I.RP$pchisq != "NaN" & I.RP$pchisq < 0.01),1])/length(I.RP[(I.RP$imor != "NaN"),1])), (length(I.NB[(I.NB$pchisq != "NaN" & I.NB$pchisq < 0.01),1])/length(I.NB[(I.NB$imor != "NaN"),1])), (length(I.CB[(I.CB$pchisq != "NaN" & I.CB$pchisq < 0.01),1])/length(I.CB[(I.CB$imor != "NaN"),1])), (length(I.BI[(I.BI$pchisq != "NaN" & I.BI$pchisq < 0.01),1])/length(I.BI[(I.BI$imor != "NaN"),1])), (length(I.CC[(I.CC$pchisq != "NaN" & I.CC$pchisq < 0.01),1])/length(I.CC[(I.CC$imor != "NaN"),1])))

I.means <- cbind(means, ci.lowers, ci.uppers, Nsig, c('DC', 'WI', 'BE', 'EI', 'RP', 'NB', 'CB', 'BI', 'CC'))
I.means <- as.data.frame(I.means)
names(I.means) <- c("Aggregation (I.m)", "CI.lower", "CI.upper","Proportion species with significant I.m","Site")

#information for Table 1:
kable(I.means, caption = "")


```

3. Rarified richness estimates for estimated species richess at the meadow scale, extrapolated to 2x the observed abundance for one sample within each meadow.
```{r}
library(iNEXT)

# create rank abundance profiles for each site (we need this for Table 2 below)
BEsp <- div.data %>%
  filter(site == "BE") %>%
  select(., -(c(1:3,38:39))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) 

rankBE <- BEsp %>%
  mutate(., rank = min_rank(desc(N)))

DCsp <- div.data %>%
  filter(site == "DC") %>%
  select(., -(c(1:3,38:39))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) 

rankDC <- DCsp %>%
  mutate(., rank = min_rank(desc(N)))

WIsp <- div.data %>%
  filter(site == "WI") %>%
  select(., -(c(1:3,38:39))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) 

rankWI <- WIsp %>%
  mutate(., rank = min_rank(desc(N)))

EIsp <- div.data %>%
  filter(site == "EI") %>%
  select(., -(c(1:3,38:39))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) 

rankEI <- EIsp %>%
  mutate(., rank = min_rank(desc(N)))

RPsp <- div.data %>%
  filter(site == "RP") %>%
  select(., -(c(1:3,38:39))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) 

rankRP <- RPsp %>%
  mutate(., rank = min_rank(desc(N)))

NBsp <- div.data %>%
  filter(site == "NB") %>%
  select(., -(c(1:3,38:39))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) 

rankNB <- NBsp %>%
  mutate(., rank = min_rank(desc(N))) 

CBsp <- div.data %>%
  filter(site == "CB") %>%
  select(., -(c(1:3,38:39))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N))

rankCB <- CBsp %>%
  mutate(., rank = min_rank(desc(N)))

BIsp <- div.data %>%
  filter(site == "BI") %>%
  select(., -(c(1:3,38:39))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) 

rankBI <- BIsp %>%
  mutate(., rank = min_rank(desc(N)))

CCsp <- div.data %>%
  filter(site == "CC") %>%
  select(., -(c(1:3,38:39))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) 

rankCC <- CCsp %>%
  mutate(., rank = min_rank(desc(N)))

ALLsp <- div.data %>%
  #filter(site == "CC") %>%
  select(., -(c(1:3,38:39))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) 

rankALL <- ALLsp %>%
  mutate(., rank = min_rank(desc(N)))

#create data input for rarified richness estimates: 
RBE <- rankBE[,2]
RRP <- rankRP[,2]
RDC <- rankDC[,2]
RWI <- rankWI[,2]
RCC <- rankCC[,2]
RCB <- rankCB[,2]
RNB <- rankNB[,2]
REI <- rankEI[,2]
RBI <- rankBI[,2]

Rd <- cbind(RBE, RRP, RDC, RWI, RCC, RCB, RNB, REI, RBI)

## Set m based on maximum observed abundance: 32164.
#m <- seq(1,32164,32164/100)
m <- seq(1,(2*7587),(2*7587)/100)

iNEXT(Rd, q= c(0), datatype="abundance", size=NULL, endpoint=NULL, knots=40, se=TRUE, conf=0.95, nboot=50) -> test

results <- rbind(test$iNextEst$RBE[40,4:6], test$iNextEst$RRP[40,4:6], test$iNextEst$RDC[40,4:6], test$iNextEst$RWI[40,4:6], test$iNextEst$RCC[40,4:6], test$iNextEst$RCB[40,4:6], test$iNextEst$RNB[40,4:6], test$iNextEst$REI[40,4:6], test$iNextEst$REI[40,4:6])
rownames(results) <- test$DataInfo[,1]
results$site <- c("BE", "RP", "DC", "WI", "CC", "CB", "NB", "EI", "BI")

#information for Table 1:
kable(results, col.names = c("Extrapolated Richness", "CI.Lower", "CI.Upper", "site"), caption = "")

```

TABLE 2. Table 2 presents each species rank within each site and time. It allows us to see whether similar species were abundant across sites and times.

First for July:

```{r}
## create datafile with ranks:
RanksJuly <- rankDC %>%
  full_join(rankWI, by = "species", suffix = c(".DC", ".WI")) %>%
  full_join(rankBE, by = "species", suffix = c("", ".BE")) %>%  
  full_join(rankEI, by = "species", suffix = c("", ".EI")) %>%
  full_join(rankRP, by = "species", suffix = c("", ".RP")) %>%
  full_join(rankNB, by = "species", suffix = c("", ".NB")) %>%
  full_join(rankCB, by = "species", suffix = c("", ".CB")) %>%  
  full_join(rankBI, by = "species", suffix = c("", ".BI")) %>%
  full_join(rankCC, by = "species", suffix = c("", ".CC")) %>%
  select(., -starts_with("N"))
View(RanksJuly)

kable(RanksJuly, col.names = c("Species", "DC", "WI", "BE", "EI", "RP",  "NB", "CB","BI", "CC"), caption = "Ranks for July species abundances (N)")

```


Then for May:
```{r}
## need to redefine div.data for May: 
start.data <- dataMAY
div.data <- dcast(start.data[,c(1:4,12)], site + Date + Sample ~ species, sum)

DCag <- div.data %>%
  filter(site == "DC") %>%
  select(., -(c(1:3))) %>%
  dispindmorisita(., unique.rm = TRUE, na.rm = TRUE) %>%
  mutate(., species = rownames(.)) %>%
  mutate(., aggregated = ifelse(pchisq < 0.05, 'Yes', 'No')) %>%
  select(., species:aggregated)

rankDC <- div.data %>%
  filter(site == "DC") %>%
  select(., -(c(1:3))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) %>%
  mutate(., rank = min_rank(desc(N))) %>%
  full_join(DCag, by = "species")

WIag <- div.data %>%
  filter(site == "WI") %>%
  select(., -(c(1:3))) %>%
  dispindmorisita(., unique.rm = TRUE, na.rm = TRUE) %>%
  mutate(., species = rownames(.)) %>%
  mutate(., aggregated = ifelse(pchisq < 0.05, 'Yes', 'No')) %>%
  select(., species:aggregated)

rankWI <- div.data %>%
  filter(site == "WI") %>%
  select(., -(c(1:3))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) %>%
  mutate(., rank = min_rank(desc(N))) %>%
  full_join(WIag, by = "species")

RPag <- div.data %>%
  filter(site == "RP") %>%
  select(., -(c(1:3))) %>%
  dispindmorisita(., unique.rm = TRUE, na.rm = TRUE) %>%
  mutate(., species = rownames(.)) %>%
  mutate(., aggregated = ifelse(pchisq < 0.05, 'Yes', 'No')) %>%
  select(., species:aggregated)

rankRP <- div.data %>%
  filter(site == "RP") %>%
  select(., -(c(1:3))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) %>%
  mutate(., rank = min_rank(desc(N))) %>%
  full_join(RPag, by = "species")

NBag <- div.data %>%
  filter(site == "NB") %>%
  select(., -(c(1:3))) %>%
  dispindmorisita(., unique.rm = TRUE, na.rm = TRUE) %>%
  mutate(., species = rownames(.)) %>%
  mutate(., aggregated = ifelse(pchisq < 0.05, 'Yes', 'No')) %>%
  select(., species:aggregated)

rankNB <- div.data %>%
  filter(site == "NB") %>%
  select(., -(c(1:3))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) %>%
  mutate(., rank = min_rank(desc(N))) %>%
  full_join(NBag, by = "species")

CBag <- div.data %>%
  filter(site == "CB") %>%
  select(., -(c(1:3))) %>%
  dispindmorisita(., unique.rm = TRUE, na.rm = TRUE) %>%
  mutate(., species = rownames(.)) %>%
  mutate(., aggregated = ifelse(pchisq < 0.05, 'Yes', 'No')) %>%
  select(., species:aggregated)

rankCB <- div.data %>%
  filter(site == "CB") %>%
  select(., -(c(1:3))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) %>%
  mutate(., rank = min_rank(desc(N))) %>%
  full_join(CBag, by = "species")

RanksMay <- rankDC %>%
  full_join(rankWI, by = "species", suffix = c(".DC", ".WI")) %>%
  full_join(rankRP, by = "species", suffix = c("", ".RP")) %>%  
  full_join(rankNB, by = "species", suffix = c("", ".NB")) %>%
  full_join(rankCB, by = "species", suffix = c("", ".CB")) %>%
  select(., -starts_with("N"))

kable(RanksMay, col.names = c("Species", "DC.rank", "DC.aggregated", "WI.rank","WI.aggregated", "RP.rank", "RP.aggregated", "NB.rank", "NB.aggregated", "CB.rank","CB.aggregated"), caption = "Ranks for May species abundances (N). Aggregated column indicates signficant (P < 0.05) spatial aggregation within species across plots within each meadow, based on chi-squared tests on Morisita's index I")


```

Then for August:
```{r}
## need to redefine div.data for Aug: 
start.data <- dataAUG
div.data <- dcast(start.data[,c(1:4,12)], site + Date + Sample ~ species, sum)

start.data <- dataMAY
div.data <- dcast(start.data[,c(1:4,12)], site + Date + Sample ~ species, sum)

DCag <- div.data %>%
  filter(site == "DC") %>%
  select(., -(c(1:3))) %>%
  dispindmorisita(., unique.rm = TRUE, na.rm = TRUE) %>%
  mutate(., species = rownames(.)) %>%
  mutate(., aggregated = ifelse(pchisq < 0.05, 'Yes', 'No')) %>%
  select(., species:aggregated)

rankDC <- div.data %>%
  filter(site == "DC") %>%
  select(., -(c(1:3))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) %>%
  mutate(., rank = min_rank(desc(N))) %>%
  full_join(DCag, by = "species")

WIag <- div.data %>%
  filter(site == "WI") %>%
  select(., -(c(1:3))) %>%
  dispindmorisita(., unique.rm = TRUE, na.rm = TRUE) %>%
  mutate(., species = rownames(.)) %>%
  mutate(., aggregated = ifelse(pchisq < 0.05, 'Yes', 'No')) %>%
  select(., species:aggregated)

rankWI <- div.data %>%
  filter(site == "WI") %>%
  select(., -(c(1:3))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) %>%
  mutate(., rank = min_rank(desc(N))) %>%
  full_join(WIag, by = "species")

RPag <- div.data %>%
  filter(site == "RP") %>%
  select(., -(c(1:3))) %>%
  dispindmorisita(., unique.rm = TRUE, na.rm = TRUE) %>%
  mutate(., species = rownames(.)) %>%
  mutate(., aggregated = ifelse(pchisq < 0.05, 'Yes', 'No')) %>%
  select(., species:aggregated)

rankRP <- div.data %>%
  filter(site == "RP") %>%
  select(., -(c(1:3))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) %>%
  mutate(., rank = min_rank(desc(N))) %>%
  full_join(RPag, by = "species")

NBag <- div.data %>%
  filter(site == "NB") %>%
  select(., -(c(1:3))) %>%
  dispindmorisita(., unique.rm = TRUE, na.rm = TRUE) %>%
  mutate(., species = rownames(.)) %>%
  mutate(., aggregated = ifelse(pchisq < 0.05, 'Yes', 'No')) %>%
  select(., species:aggregated)

rankNB <- div.data %>%
  filter(site == "NB") %>%
  select(., -(c(1:3))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) %>%
  mutate(., rank = min_rank(desc(N))) %>%
  full_join(NBag, by = "species")

CBag <- div.data %>%
  filter(site == "CB") %>%
  select(., -(c(1:3))) %>%
  dispindmorisita(., unique.rm = TRUE, na.rm = TRUE) %>%
  mutate(., species = rownames(.)) %>%
  mutate(., aggregated = ifelse(pchisq < 0.05, 'Yes', 'No')) %>%
  select(., species:aggregated)

rankCB <- div.data %>%
  filter(site == "CB") %>%
  select(., -(c(1:3))) %>%
  summarise_all(., funs(sum)) %>%
  tidyr::gather(., "species", "N") %>%
  arrange(., desc(N)) %>%
  mutate(., rank = min_rank(desc(N))) %>%
  full_join(CBag, by = "species")

RanksAug <- rankDC %>%
  full_join(rankWI, by = "species", suffix = c(".DC", ".WI")) %>%
  full_join(rankRP, by = "species", suffix = c("", ".RP")) %>%  
  full_join(rankNB, by = "species", suffix = c("", ".NB")) %>%
  full_join(rankCB, by = "species", suffix = c("", ".CB")) %>%
  select(., -starts_with("N"))

kable(RanksAug, col.names = c("Species", "DC.rank", "DC.aggregated", "WI.rank","WI.aggregated", "RP.rank", "RP.aggregated", "NB.rank", "NB.aggregated", "CB.rank","CB.aggregated"), caption = "Ranks for May species abundances (N). Aggregated column indicates signficant (P < 0.05) spatial aggregation within species across plots within each meadow, based on chi-squared tests on Morisita's index I")
```


Estimation of univariate diversity indices and rank abundance distributions
Results for main text
```{r}
start.data <- dataJULY9
div.data <- dcast(start.data[,c(1:4,12)], site + Date + Sample ~ species, sum) 
div.data$alpha.p <- specnumber(div.data[,4:37])
div.data$N <- rowSums(div.data[,(4:37)])

## estimate univariate diversity for each sample
div.summary <- div.data[c(1:3, 38:39)] %>%
  mutate(., H = diversity(div.data[,-(c(1:3))], index ="shannon")) %>%
  mutate(., S = diversity(div.data[,-(c(1:3))], index ="simpson")) %>%
  full_join(sites, by = "site") %>%
  full_join(I.means, by = c("site" = "Site")) %>%
  full_join(site.alpha, by = "site") %>%
  full_join(results, by = "site")
  #mutate(., apB = as.numeric(as.character(alpha) - as.numeric(as.character(alpha.p))))

```

Statistical analysis: Spatial diversity patterns
Does plot level alpha diversity differ among meadows?
```{r}
# does plot level alpha diversity differ among meadows?
mods4 <- lm(div.summary$alpha.p ~ div.summary$site)
mods0 <-  lm(div.summary$alpha.p ~ 1)
anova(mods4, mods0)
model.sel(mods4, mods0)
summary(mods4)
```

Does plot level Shannon diversity differ among meadows?
```{r}
# does plot level alpha diversity differ among meadows?
mods3 <- lm(div.summary$H ~ div.summary$site)
mods0 <-  lm(div.summary$H ~ 1)
anova(mods3, mods0)
model.sel(mods3, mods0)
summary(mods3)
```


#Model selection - presented in Table S5
```{r}
#candidate models
mod1a <- lm(div.summary$H ~ div.summary$fetch.jc)
mod2a <- lm(div.summary$S ~ div.summary$fetch.jc)
mod3a <- lm(div.summary$alpha.p ~ div.summary$fetch.jc)
mod4a <- lm(div.summary$qD ~ div.summary$fetch.jc)

mod1b <- lm(div.summary$H ~ div.summary$dfw)
mod2b <- lm(div.summary$S ~ div.summary$dfw)
mod3b <- lm(div.summary$alpha.p ~ div.summary$dfw)
mod4b <- lm(div.summary$qD ~ div.summary$dfw)

mod1c <- lm(div.summary$H ~ div.summary$dfw * div.summary$fetch.jc)
mod2c <- lm(div.summary$S ~ div.summary$dfw * div.summary$fetch.jc)
mod3c <- lm(div.summary$alpha.p ~ div.summary$dfw * div.summary$fetch.jc)
mod4c <- lm(div.summary$qD ~ div.summary$dfw * div.summary$fetch.jc)

mod1f <- lm(div.summary$H ~ div.summary$area * div.summary$fetch.jc)
mod2f <- lm(div.summary$S ~ div.summary$area * div.summary$fetch.jc)
mod3f <- lm(div.summary$alpha.p ~ div.summary$area * div.summary$fetch.jc)
mod4f <- lm(div.summary$qD ~ div.summary$area * div.summary$fetch.jc)

mod1d <- lm(div.summary$H ~ 1)
mod2d <- lm(div.summary$S ~ 1)
mod3d <- lm(div.summary$alpha.p ~ 1)
mod4d <- lm(div.summary$qD ~ 1)

mod1g <- lm(div.summary$H ~ div.summary$site)
mod2g <- lm(div.summary$S ~ div.summary$site)
mod3g <- lm(div.summary$alpha.p ~ div.summary$site)
mod4g <- lm(div.summary$qD ~ div.summary$site)
```

Model comparison results for Shannon Diversity in Table S5
```{r}
model.sel(mod1a, mod1b, mod1c, mod1d, mod1f, mod1g)
```

Model comparison results for Simpson Diversity in Table S5
```{r}
model.sel(mod2a, mod2b, mod2c, mod2d, mod2f, mod2g)
```

Model comparison results for Alpha Diversity in Table S5
```{r}
model.sel(mod3a, mod3b, mod3c, mod3d, mod3f, mod3g)
```

Model comparison results for rarefied Diversity in Table S5
```{r}
model.sel(mod4a, mod4b, mod4c, mod4d, mod4f, mod4g)
```

